Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Add missing \noindent statements

First, we introduce a new Haddock markup for the example.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

To specify properties, we also propose a new markup. In this paper, we use the {\tt prop>} prefix. We can write properties which do not take parameters as follows:

@@

Examples and properties in comments are automatically
tested by the Doctest command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

>>>>

\noindent First, we introduce a new Haddock markup for the example.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent To specify properties, we also propose a new markup. In this paper, we
use the {\tt prop>} prefix. We can write properties which do not take
parameters as follows:

@@

\noindent Examples and properties in comments are automatically
tested by the Doctest command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.
